Supplement: A Continuous Occlusion Model for Road Scene Understanding

### 2017-12-01 CVPR16/Source/applications.tex
Changing noration to match rest of the document.

\newcommand\RotText[1]{\rotatebox{90}{\parbox{1.7cm}{\centering#1}}}
\begin{wraptable}[16]{r}{0.5\textwidth}
\centering\footnotesize
\begin{tabular}{|l|l|l|}
\hline
 & Symbol & Description \\
\hline
\hline
\multirow{2}{*}{\rotatebox{90}{Input}} & $\bu_j(t)$ & 2D feature track $j$ at time $t$ \\
 & $\bb{i}$ & 2D detection bounding box of object $O_i$ at time $t$ \\
\hline
\hline
\multirow{5}{*}{\RotText{Initialization with~\cite{Song_Chandraker_2014}}} & $\bp^c(t)$ & Position of camera at time $t$ \\
 & $\bomega^c(t)$ & Orientation of camera at time $t$ \\
 & $\bp_0^i(t)$ & Initial position of object $O_i$ at time $t$ \\
 & $\bomega_0^i(t)$ & Initial orientation of object $O_i$ at time $t$ \\
 & $\bB_0^i$ & Initial 3D dimensions of object $O_i$ \\
\hline
\hline
\multirow{4}{*}{\rotatebox{90}{Output}} & $P^{ij}_{\text{assoc}}$ & Probability of assigning feature track $j$ to object $O_i$ \\	
 & $\bp^i(t)$ & Position of object $O_i$ at time $t$ \\
 & $\bomega^i(t)$ & Orientation of object $O_i$ at time $t$ \\
 & $\bB^i$ & 3D dimensions of object $O_i$ \\
\hline
\end{tabular}
\vspace{-0.25cm}
\caption{Notation of inputs and outputs for object-point association and 3D object localization. Note that object dimensions are independent of time.}
\label{tab:notations}
\vspace{-0.5cm}
\end{wraptable}

@@

Given 2D image points $\{\bu_j\}$ that are tracked between consecutive frames and a set of objects $\{O_i\}$ appearing in the frames, we aim to associate $\bu_j$ with $O_i$. Based on our continuous occlusion model in Section~\ref{sec:setup}, the association probability $\assocP$ between point track $\bu_j$ and object $O_i$ at depth $\lambda$ can be defined as
\begin{align}
\assocP = \Prefl\Ptrans,
\label{eq:defineassocP}
\end{align}
where $\Prefl$ and $\Ptrans$ are from \eqref{eq:evalPrefl} and \eqref{eq:evalCumulativePtrans} respectively. Note that the fraction $\assocP$, although called association probability, does not capture the entire information that we have available for computing the association of point tracks to objects.

Rather, to compute the association probability between point track $\bu_j$ and object $O_i$, we should also use the reprojection error. When the association of point track $\bu_j$ and object $O_i$ is correct and the point of reflection is at depth $\lambda$, the corresponding reprojection error $\Ereproj(\lambda)$ must be zero, otherwise the error becomes a measure of distance from the true solution. The error $\Ereproj(\lambda)$ can be used for associating point tracks and objects by converting it to the probability domain as
\begin{align}
  P^{ij}_{\text{reproj}}(\lambda) = \frac{1}{Z'}\exp(-\Ereproj(\lambda)),
\label{eq:Passocbyreproj}
\end{align}
where $Z'$ is the normalization coefficient.

Using both of the evidence terms in \eqref{eq:defineassocP} and \eqref{eq:Passocbyreproj}, we can define the new association probability $P^{ij}_{\text{assoc}}$, as follows:
\begin{align}
  P^{ij}_{\text{assoc}} = \frac{1}{Z''}\int_0^{\infty} \assocP \exp(-\Ereproj(\lambda))d\lambda,
  \label{eq:prob-assoc}
\end{align}
where $Z''$ is the new normalization coefficient.

Once we have computed the association probability $P^{ij}_{\text{assoc}}$ for every pair of point tracks and objects, we can assign each point track to the object with the highest association probability. The point tracks having very small association probabilities are assigned to the background.

@@

\begin{wrapfigure}[22]{r}{0.5\textwidth}
  \centering
  \begin{tabular}{c}
    \newcommand{\imagewidth}{7.5cm}
      \hspace{-0.8cm}
    \input{Source/scenelayoutoverlayCity0961} \\
      \hspace{-0.8cm}
    \input{Source/graphical_model_multiple}
  \end{tabular}
  \caption{\small (Top) A sample road scene with occlusions, where the unknowns of each object are modeled as random variables. (Bottom) The graphical model corresponding to the above frame. In particular, the numbered nodes denote the unknown state variables of each object (position, orientation, and dimensions), the shaded nodes are observed variables (detection bounding boxes and point tracks), and the colored squares represent various energies that capture object-object interactions.}
  \label{fig:graphmodel}
\end{wrapfigure}

In this section, we exploit our continuous occlusion model for another application, namely, 3D object localization in road scenes, which further demonstrates its versatility. Given a set of 2D tracked feature points $\{\bu_j(t)\}$ and 2D detection bounding boxes $\{\bb{i}\}$ at frame $t$, the goal is to localize 3D traffic participants. In particular, for each traffic participant, we wish to estimate its position $\bp^i(t)$ and orientation $\bomega^i(t)$ on the ground plane and its 3D dimensions $\bB^i(t)$. Please refer to Table~\ref{tab:notations} for a summary of inputs and outputs.

We construct a graphical model for representing relationships among objects, as well as between objects and point tracks. Figure~\ref{fig:graphmodel} illustrates an example of the graph and energies. The negative log likelihood is decomposed as follows:
%
\begin{multline*}
  -\log{P(\{ \bp^i(t) , \bomega^i(t) , \bB^i(t) \} | \{\bu_j(t)\} , \{\bb{i}\} )} = \\
  -\tilde{Z} 
  + \sum_{t=s_i}^{e_i} \lambda_{\text{track}}\EnergyTrack
  + \\ 
  \sum_{t=s_i}^{e_i} \sum_{i=1}^N  
  \left(
    \lambda_{\text{detect}}\EnergyBBox
    + \lambda_{\text{dyn}}\EnergyDyn    
    + \lambda_{\text{size}}\EnergySize
  \right)
  \enspace,
\end{multline*}
%
where $\pEnergy{track}$ and $\Energy{detect}$ reason about image observations such as point tracks and bounding boxes, while $\Energy{dyn}$  and $\Energy{size}$ impose smoothness constraints and size priors respectively. Here, $\lambda_{\text{track}}$, $\lambda_{\text{detect}}$, $\lambda_{\text{dyn}}$, $\lambda_{\text{size}}$ are energy weights, $N$ is the number of objects in the sequence, $s_i$ and $t_i$ are respectively the starting and ending frames of object $O_i$, and $\tilde{Z}$ is the normalization coefficient. Next, we present our unified continuous occlusion modeling for both point track and bounding box energies. Due to space constraints, we present the details of other energies in the supplementary material.

\vspace{-0.3cm}
\paragraph{Continuous point track energy with occlusion}
%\label{sec:totalContPtTracksEnergy}
Let $\relp{i}{t}$ be the pose of object $O_i$ at time $t$ in world coordinates, which is computed using the camera pose at time $t$ and the relative pose of object $O_i$ with respect to the camera at time $t$. We denote $\projectionOf{.}$ and $\invProjectionOftm{.}$ as the forward and inverse projection functions that project a 3D point to the 2D image and vice versa. Then, the reprojection error for 2D point $\trackp{t}$ with hypothesized depth $\lambda$, is given by
\begin{equation}
\Ereproj(\lambda) = \left\|\trackpj{t} - \projectionOf{\invProjectionOftm{\trackpj{t-1}, \lambda}}\right\|^2.
\label{eq:reprojerror}
\end{equation}
Note that the inverse projection $\invProjectionOf{.}$ depends on both the 2D point $\trackp{t}$ and the unknown depth $\lambda$. Also note that the inverse projection relies on the object pose at time $t-1$ while the forward projection relies on the object pose at time $t$, which can be different.

For an object $O_i$, let $\{ \Omega (t) \}_i$ be the poses of all occluding objects at time $t$ (inclusive of object $O_i$) and $ \{ \bB \}_i$ be their corresponding 3D dimensions. Then, we model the continuous point track energy with explicit occlusion reasoning as the expected reprojection error over the association probability
\begin{align}
  %\!\!\!\! \Energy{track}(\relp{i}{t}, \relp{i}{t-1}, \dimsn{i}, \{ \Omega (t) \}_i, \{ \Omega (t-1) \}_i, \{ \bB \}_i ) 
  %\Energy{track}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = 
  \pEnergy{track}(\{ \Omega (t) \}_i, \{ \Omega (t-1) \}_i, \{ \bB \}_i )
  %\\
    = \sum_{i=1}^{N} 
    %\sum_{t = s_i}^{e_i}
    \sum_{j = 1}^{M}
    \int_0^\infty \assocP\Ereproj(\lambda) d\lambda,
\end{align}
where $N$ and $M$ are, respectively, the number of objects and points and $\assocP$ is the association probability of point $\trackp{t}$ with object $O_i$ at depth $\lambda$, given by \eqref{eq:defineassocP}.

>>>>

\newcommand\RotText[1]{\rotatebox{90}{\parbox{1.7cm}{\centering#1}}}
\begin{wraptable}[16]{r}{0.5\textwidth}
\centering\footnotesize
\begin{tabular}{|l|l|p{0.32\textwidth}|}
\hline
 & Symbol & Description \\
\hline
\hline
\multirow{2}{*}{\rotatebox{90}{Input}} & $\impt_j(t)$ & 2D feature track $j$ at time $t$ \\
 & $\bb{i}$ & 2D detection bounding box of object $\Obj_i$ at time $t$ \\
\hline
\hline
\multirow{5}{*}{\RotText{Initialization with~\cite{Song_Chandraker_2014}}} & $\camO(t)$ & Position of camera at time $t$ \\
 & $\camR(t)$ & Orientation of camera at time $t$ \\
 & $\ObjMu_0^i(t)$ & Initial position of object $\Obj_i$ at time $t$ \\
 & $\ObjR_0^i(t)$ & Initial orientation of object $\Obj_i$ at time $t$ \\
 & $\BB_0^i$ & Initial 3D dimensions of object $\Obj_i$ \\
\hline
\hline
\multirow{4}{*}{\rotatebox{90}{Output}} & $\PassocR$ & Probability of assigning feature track $j$ to object $\Obj_i$ \\	
 & $\ObjMu^i(t)$ & Position of object $\Obj_i$ at time $t$ \\
 & $\ObjR^i(t)$ & Orientation of object $\Obj_i$ at time $t$ \\
 & $\BB^i$ & 3D dimensions of object $\Obj_i$ \\
\hline
\end{tabular}
\vspace{-0.25cm}
\caption{Notation of inputs and outputs for object-point association and 3D object localization. Note that object dimensions are independent of time.}
\label{tab:notations}
\vspace{-0.5cm}
\end{wraptable}

@@

Given 2D image points $\{\impt_j\}$ that are tracked between consecutive frames and a set of objects $\{\Obj_i\}$ appearing in the frames, we aim to associate $\impt_j$ with $\Obj_i$. Based on our continuous occlusion model in Section~\ref{sec:setup}, the association probability $\assocP$ between point track $\impt_j$ and object $\Obj_i$ at depth $\lambda$ can be defined as
\begin{align}
\assocP = \Prefl\Ptrans,
\label{eq:defineassocP}
\end{align}
where $\Prefl$ and $\Ptrans$ are from \eqref{eq:evalPrefl} and \eqref{eq:evalCumulativePtrans} respectively. Note that the fraction $\assocP$, although called association probability, does not capture the entire information that we have available for computing the association of point tracks to objects.

Rather, to compute the association probability between point track $\impt_j$ and object $\Obj_i$, we should also use the reprojection error. When the association of point track $\impt_j$ and object $\Obj_i$ is correct and the point of reflection is at depth $\lambda$, the corresponding reprojection error $\Ereproj(\lambda)$ must be zero, otherwise the error becomes a measure of distance from the true solution. The error $\Ereproj(\lambda)$ can be used for associating point tracks and objects by converting it to the probability domain as
\begin{align}
  P^{ij}_{\text{reproj}}(\lambda) = \frac{1}{Z'}\exp(-\Ereproj(\lambda)),
\label{eq:Passocbyreproj}
\end{align}
where $Z'$ is the normalization coefficient.

Using both of the evidence terms in \eqref{eq:defineassocP} and \eqref{eq:Passocbyreproj}, we can define the new association probability $P^{ij}_{\text{assoc}}$, as follows:
\begin{align}
  \PassocR = \frac{1}{Z''}\int_c^{\infty} \assocP \exp(-\Ereproj(\lambda))d\lambda,
  \label{eq:prob-assoc}
\end{align}
where $Z''$ is the new normalization coefficient.

\begin{wrapfigure}[18]{r}{0.5\textwidth}
  \centering\scriptsize
  \begin{tabular}{c}
    \newcommand{\imagewidth}{7.5cm}
      \hspace{-0.8cm}
    \input{Source/scenelayoutoverlayCity0961} \\
      \hspace{-0.8cm}
    \input{Source/graphical_model_multiple}
  \end{tabular}
  \caption{(Top) A sample road scene with occlusions, where the unknowns of each object are modeled as random variables. (Bottom) The graphical model corresponding to the above frame. In particular, the numbered nodes denote the unknown state variables of each object (position, orientation, and dimensions), the shaded nodes are observed variables (detection bounding boxes and point tracks), and the colored squares represent various energies that capture object-object interactions.}
  \label{fig:graphmodel}
\end{wrapfigure}
%

Once we have computed the association probability $\PassocR$ for every pair of point tracks and objects, we can assign each point track to the object with the highest association probability. The point tracks having very small association probabilities are assigned to the background.

@@

In this section, we exploit our continuous occlusion model for another application, namely, 3D object localization in road scenes, which further demonstrates its versatility. Given a set of 2D tracked feature points $\{\impt_j(t)\}$ and 2D detection bounding boxes $\{\bb{i}\}$ at frame $t$, the goal is to localize 3D traffic participants. In particular, for each traffic participant, we wish to estimate its position $\ObjMu^i(t)$ and orientation $\ObjR^i(t)$ on the ground plane and its 3D dimensions $\BB^i(t)$. Please refer to Table~\ref{tab:notations} for a summary of inputs and outputs.

We construct a graphical model for representing relationships among objects, as well as between objects and point tracks. Figure~\ref{fig:graphmodel} illustrates an example of the graph and energies. The negative log likelihood is decomposed as follows:
%
\begin{multline*}
  -\log{P(\{ \ObjMu^i(t) , \ObjR^i(t) , \BB^i(t) \} | \{\impt_j(t)\} , \{\bb{i}\} )} = \\
  -\tilde{Z} 
  + \sum_{t=s_i}^{e_i} \lambda_{\text{track}}\EnergyTrack
  + \\ 
  \sum_{t=s_i}^{e_i} \sum_{i=1}^N  
  \left(
    \lambda_{\text{detect}}\EnergyBBox
    + \lambda_{\text{dyn}}\EnergyDyn    
    + \lambda_{\text{size}}\EnergySize
  \right)
  \enspace,
\end{multline*}
%
where $\pEnergy{track}$ and $\Energy{detect}$ reason about image observations such as point tracks and bounding boxes, while $\Energy{dyn}$  and $\Energy{size}$ impose smoothness constraints and size priors respectively. Here, $\lambda_{\text{track}}$, $\lambda_{\text{detect}}$, $\lambda_{\text{dyn}}$, $\lambda_{\text{size}}$ are energy weights, $N$ is the number of objects in the sequence, $s_i$ and $t_i$ are respectively the starting and ending frames of object $\Obj_i$, and $\tilde{Z}$ is the normalization coefficient. Next, we present our unified continuous occlusion modeling for both point track and bounding box energies. Due to space constraints, we present the details of other energies in the supplementary material.

\vspace{-0.3cm}
\paragraph{Continuous point track energy with occlusion}
%\label{sec:totalContPtTracksEnergy}
Let $\relp{i}{t}$ be the pose of object $\Obj_i$ at time $t$ in world coordinates, which is computed using the camera pose at time $t$ and the relative pose of object $\Obj_i$ with respect to the camera at time $t$. We denote $\projectionOf{.}$ and $\invProjectionOftm{.}$ as the forward and inverse projection functions that project a 3D point to the 2D image and vice versa. Then, the reprojection error for 2D point $\trackp{t}$ with hypothesized depth $\lambda$, is given by
\begin{equation}
\Ereproj(\lambda) = \left\|\trackpj{t} - \projectionOf{\invProjectionOftm{\trackpj{t-1}, \lambda}}\right\|^2.
\label{eq:reprojerror}
\end{equation}
Note that the inverse projection $\invProjectionOf{.}$ depends on both the 2D point $\trackp{t}$ and the unknown depth $\lambda$. Also note that the inverse projection relies on the object pose at time $t-1$ while the forward projection relies on the object pose at time $t$, which can be different.

For an object $\Obj_i$, let $\{ \posealt (t) \}_i$ be the poses of all occluding objects at time $t$ (inclusive of object $\Obj_i$) and $ \{ \BB \}_i$ be their corresponding 3D dimensions. Then, we model the continuous point track energy with explicit occlusion reasoning as the expected reprojection error over the association probability
\begin{align}
  %\!\!\!\! \Energy{track}(\relp{i}{t}, \relp{i}{t-1}, \dimsn{i}, \{ \Omega (t) \}_i, \{ \Omega (t-1) \}_i, \{ \bB \}_i ) 
  %\Energy{track}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = 
  \pEnergy{track}(\{ \posealt (t) \}_i, \{ \posealt (t-1) \}_i, \{ \BB \}_i )
  %\\
    = \sum_{i=1}^{N} 
    %\sum_{t = s_i}^{e_i}
    \sum_{j = 1}^{M}
    \int_0^\infty \assocP\Ereproj(\lambda) d\lambda,
\end{align}
where $N$ and $M$ are, respectively, the number of objects and points and $\assocP$ is the association probability of point $\trackp{t}$ with object $\Obj_i$ at depth $\lambda$, given by \eqref{eq:defineassocP}.

### 2017-12-01 CVPR16/Source/contBBoxModel.tex
Fit into the phdpropoal single column format.
Changing noration to match rest of the document.

\vspace{-0.3cm}
\paragraph{Continuous bounding box energy with occlusion}
Object detection is usually followed by non-maximal suppression that results in discarding similar bounding boxes. When we are jointly optimizing detections with other cues, it is usually not desirable to use a single bounding box. To retain the entire detection output while maintaining the continuous form of our energies, we approximate the distribution of detection scores with a multi-modal sum of Gaussian-like logistic functions. In particular, let 2D bounding box $\bb{i}$ be parameterized as a 4D vector $[\minx, \miny, \maxx, \maxy]^\top$. We fit a parametric function to the detection scores, of the form
\begin{equation}
S(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{i}(t)^\top \bLambda_k^{-1} \bepsilon_k^{i}(t) \right),
\label{eq:GMMscores}
\end{equation}
where $A_k$ is an amplitude and $\bepsilon_k^{i}(t) = \bb{i}-\bmu_k$, with $\bmu_k$ the mean and $\bLambda_k$ the covariance.
%% %
%% \begin{multline}
%%   S(\bb{i}) = \\
%%   \sum_k A_k \exp(-(\bb{i}-\mu^{(d)}_k)^\top \Sigma^{(d)-1}_k
%%   (\bb{i}-\mu^{(d)}_k))
%% \end{multline}
%% %
%% to detection scores, by 
We use a non-linear solver to minimize the above, with initialization from non-maximal suppressed outputs. The optimization is constrained by the symmetry and positive definiteness of $\bLambda_k$, $\maxx \ge \minx$ and $\maxy \ge \miny$.
%Here $\mu^{(d)}_j$ is one of the $k$ modes as a 4D vector representing a single bounding box as $[\minx, \miny, \maxx, \maxy]^\top$. The optimization is constrained with symmetry and positive definiteness of $\Sigma^{(d)-1}_k$, $\maxx \ge \minx$ and $\maxy \ge \miny$.

\paragraph{Detection scores with occlusion reasoning} 
\def\u{\mathbf{u}}
With our model of $\Ptrans$ described in Section \ref{sec:ptransmission}, we 
compute the probability of a point $\u$ in the image to be occluded, assuming
the point is on object $O_i$ with mean depth $\meandepth{i}$, as
\begin{align}
  \Theta_{i}(\u, \meandepth{i}) = 1 - \Ptransmission(\meandepth{i}, \u).
\end{align}
If a portion of the proposed detection bounding box is known to be 
occluded, one would like to decrease the confidence in the detection score 
about the localization of that end of the object. Assuming that occlusions 
are more likely on the boundaries of the detection bounding box, we wish to decrease the 
confidence on the mean detection boundaries around the occluded boundaries.
To re-model detection scores scaled by continuous occlusion, we sample
$\Theta_{i}(\mathbf{u}, \meandepth{i})$ at the hypothesized detection boundaries from
the Gaussian mixture model (GMM) $S(.)$ in \eqref{eq:GMMscores} and augment the detection boundary covariance matrix by
$\mathcal{P}_{i} = \rho_{i}\rho_{i}^\top$, where $\rho_{i} = \Theta_{i}(\mathbf{u},
\meandepth{i})$. The new covariance matrix for the detection scores is given by 
  $\bLambda'_k = \mathcal{P}_{i} + \bLambda_k$ for all $k$.
The detection score GMM $S'(.)$ with explicit occlusion reasoning is given by replacing the covariance
matrix, as follows:
%
\begin{multline}
S'(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{i}(t)^\top \bLambda_k^{'-1} \bepsilon_k^{i}(t) \right).
\end{multline}

>>>>

\vspace{-0.3cm}
\paragraph{Continuous bounding box energy with occlusion}
Object detection is usually followed by non-maximal suppression that results in discarding similar bounding boxes. When we are jointly optimizing detections with other cues, it is usually not desirable to use a single bounding box. To retain the entire detection output while maintaining the continuous form of our energies, we approximate the distribution of detection scores with a multi-modal sum of Gaussian-like logistic functions. In particular, let 2D bounding box $\bb{i}$ be parameterized as a 4D vector $[\minx, \miny, \maxx, \maxy]^\top$. We fit a parametric function to the detection scores, of the form
\begin{equation}
S(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{i}(t)^\top \bbS_k^{-1} \bepsilon_k^{i}(t) \right),
\label{eq:GMMscores}
\end{equation}
where $A_k$ is an amplitude and $\bepsilon_k^{i}(t) = \bb{i}-\bbMu_k$, with $\bbMu_k$ the mean and $\bbS_k$ the covariance.
%% %
%% \begin{multline}
%%   S(\bb{i}) = \\
%%   \sum_k A_k \exp(-(\bb{i}-\mu^{(d)}_k)^\top \Sigma^{(d)-1}_k
%%   (\bb{i}-\mu^{(d)}_k))
%% \end{multline}
%% %
%% to detection scores, by 
We use a non-linear solver to minimize the above, with initialization from non-maximal suppressed outputs. The optimization is constrained by the symmetry and positive definiteness of $\bbS_k$, $\maxx \ge \minx$ and $\maxy \ge \miny$.
%Here $\mu^{(d)}_j$ is one of the $k$ modes as a 4D vector representing a single bounding box as $[\minx, \miny, \maxx, \maxy]^\top$. The optimization is constrained with symmetry and positive definiteness of $\Sigma^{(d)-1}_k$, $\maxx \ge \minx$ and $\maxy \ge \miny$.

\paragraph{Detection scores with occlusion reasoning} 
With our model of $\Ptrans$ described in Section \ref{sec:ptransmission}, we 
compute the probability of a point $\impt$ in the image to be occluded, assuming
the point is on object $\Obj_i$ with mean depth $\meandepth{i}$, as
\begin{align}
  \Theta_{i}(\impt, \meandepth{i}) = 1 - \PtransR(\meandepth{i}, \impt).
\end{align}
If a portion of the proposed detection bounding box is known to be 
occluded, one would like to decrease the confidence in the detection score 
about the localization of that end of the object. Assuming that occlusions 
are more likely on the boundaries of the detection bounding box, we wish to decrease the 
confidence on the mean detection boundaries around the occluded boundaries.
To re-model detection scores scaled by continuous occlusion, we sample
$\Theta_{i}(\impt, \meandepth{i})$ at the hypothesized detection boundaries from
the Gaussian mixture model (GMM) $S(.)$ in \eqref{eq:GMMscores} and augment the detection boundary covariance matrix by
$\mathcal{P}_{i} = \rho_{i}\rho_{i}^\top$, where $\rho_{i} = \Theta_{i}(\mathbf{u},
\meandepth{i})$. The new covariance matrix for the detection scores is given by 
  $\bbS'_k = \mathcal{P}_{i} + \bbS_k$ for all $k$.
The detection score GMM $S'(.)$ with explicit occlusion reasoning is given by replacing the covariance
matrix, as follows:
%
\begin{align}
S'(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{i}(t)^\top \bbS_k^{'-1} \bepsilon_k^{i}(t) \right).
\end{align}
